A New Metric for the Analysis of Swarms

### 2018-06-13 paper.tex
Section Update

\section{Calculating distance internal movement}
Equation~(\ref{eq:SwarmStabilityDistance1}) computes the mean distance of an agent to its neighbours $nbr(b)$. 
%% The relative position vector generated for an agent $b$ to its neighbour $b'$, $bb'$, is shown in~(\ref{eq:FlyToCentre1}). The magnitude of that vector gives the distance between two agents. For an individual agent the average magnitude $\mu_d(b)$ is calculated as \ref{eq:SwarmStabilityDistance1} where $b$ is the agent and $|nbr(b)|$ is the number of neighbours.

@@

\section{Cohesion/repulsion internal movement model}\label{Section:StabilityModel}
Section~\ref{Section:StabilityMagnitude}~discussed calculation of resultant cohesion~(\ref{eq:FlyToCentre1}) and resultant repulsion~(\ref{eq:Repulsion1}) vectors for each agent deriving a combined \emph{cohesion/repulsion vector} using~(\ref{eq:InterAgentMovement2}).

>>>>

% \section{Calculating distance internal movement}
Equation~(\ref{eq:SwarmStabilityDistance1}) computes the mean distance of an agent to its neighbours $nbr(b)$. 
%% The relative position vector generated for an agent $b$ to its neighbour $b'$, $bb'$, is shown in~(\ref{eq:FlyToCentre1}). The magnitude of that vector gives the distance between two agents. For an individual agent the average magnitude $\mu_d(b)$ is calculated as \ref{eq:SwarmStabilityDistance1} where $b$ is the agent and $|nbr(b)|$ is the number of neighbours.

@@

% \section{Cohesion/repulsion internal movement model}\label{Section:StabilityModel}
Section~\ref{Section:StabilityMagnitude}~discussed calculation of resultant cohesion~(\ref{eq:FlyToCentre1}) and resultant repulsion~(\ref{eq:Repulsion1}) vectors for each agent deriving a combined \emph{cohesion/repulsion vector} using~(\ref{eq:InterAgentMovement2}).
